Are kelp forests different? A comparison of kelp forests between contrasting

### 2018-09-20 paper_draft.Rmd
script additions and house cleaning

---
title: Are kelp forests different? A comparison of kelp forests between contrasting
  study sites
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    fig_caption: yes
    fig_height: 5
    fig_width: 4
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
bibliography: mycollection.bib
---

>>>>

---
title: Are kelp forests different? A comparison of kelp forests between contrasting
  study sites
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    fig_caption: yes
    fig_height: 5
    fig_width: 4
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---
